---
title: "Introduction to epivizrStandalone"
author: "Héctor Corrada Bravo"
date: "`r Sys.Date()`"
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Introduction to epivizrStandalone}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

[`Epiviz`](http://epiviz.cbcb.umd.edu) is an interactive visualization tool for functional genomics data. It supports genome navigation like other genome browsers, but allows multiple visualizations of data within genomic regions using scatterplots, heatmaps and other user-supplied visualizations. You can find more information about Epiviz at [http://epiviz.cbcb.umd.edu/help](http://epiviz.cbcb.umd.edu/help) and see a video tour [here](http://youtu.be/099c4wUxozA).

<iframe width="480" height="360" src="http://www.youtube.com/embed/099c4wUxozA" frameborder="1" allowfullscreen></iframe>

This package, `r Biocpkg("epivizrStandalone")`, makes it possible to run the web app UI locally completely within R. The `r Biocpkg("epivizr")` package implements two-way communication between the `R/Bioconductor` computational genomics environment and `Epiviz`. Objects in an `R` session can be displayed as tracks or plots on Epiviz. Epivizr uses Websockets for communication between the browser Javascript client and the R environmen, the same technology underlying the popular [Shiny](http://www.rstudio.com/shiny/) system for authoring interactive web-based reports in R. See the `r Biocpkg("epivizr")` package
vignette for more information on how to interact with the epiviz JS app.

Running the epiviz visualization app as a standalone allows it 
to browse any genome of interest using Bioconductor infrastructure. 
For example, to browse the mouse genome we would do the following.

```{r,eval=FALSE,echo=TRUE}
library(epivizrStandalone)
library(Mus.musculus)

app <- startStandalone(Mus.musculus, keep_seqlevels=paste0("chr",c(1:19,"X","Y")), verbose=TRUE, use_viewer_option = TRUE)	
```

```{r,eval=TRUE,echo=FALSE,message=FALSE}
library(epivizrStandalone)
library(Mus.musculus)

app <- startStandalone(seqinfo=seqinfo(Mus.musculus), keep_seqlevels=paste0("chr",c(1:19,"X","Y")),
                       non_interactive=TRUE, try_ports=TRUE)

app$server$start_server()	
```

```{r}
app$stop_app()
```